THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY.

### 2016-09-13 DishReflectometry/Paper1_v3.tex

% XXX document map
The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  ~\citep{Parsons_Backer_2009},\citep{Parsons_et_al_2012}, computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as the delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across a wide frequency bandwidth, the delay spectrum consists of the instrument response, the foreground signal, and the 21cm power spectrum, hereafter referred to as the EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay, $\tau = b/c$, corresponding to the given baseline length. Such techniques also assume a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuations over small scales, such as the EoR signal, and therefore, could be detectable. The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and, thus, influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over into higher delays and, thus, push the upper limit of the foreground and systematics contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scales will be lost. \\
\indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
In this paper, we investigate the performance of an individual HERA element and the resulting manifestation of the instrument response to the delay spectrum. Reflectometry measurements  are carried out across a wide bandwidth on a prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the results are interpreted in light of the delay spectrum technique of power spectrum estimation and inverse covariance weighting method of foreground suppression. Section 2 briefly describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer. Section 3 describes the reflectometry measurements and establishes the connection between visibility measurements and reflectometry. Reflectometry results are described in section 5. Section 6 evaluates the performance of the HERA element for detection of the 21~cm power spectrum.
This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}. We compare 
reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}. 
\begin{figure*}
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
\caption{HERA dish feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure*}

@@

\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER. Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it is reflected back into the space.
However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed.
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum. 
In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum in detail. We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{Antenna Reception With Multiple Reflections}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, we can think of the system as a screen at a distance $F$ from a feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally, however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\label{eq6}
\end{eqnarray}

@@

Reflectometry measurements are carried out at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016. \\
%A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.

@@

\section{\textbf{Results}}
%Return loss measurements yields the instrument pass band response that would manifest in autocorrelation data of a single HERA element. Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$. 
Performance of the HERA feed and the dish-feed assembly has been simulated by the em solver "High Frequency Structural Simulator(HFSS)" using the finite element method. 
The simulated and measured return loss of the feed, both magnitude and phase are shown in the upper panel of the figure \ref{RL_mag_dish}. While the simulated return loss of the feed structure shows two resonant peaks around 120 and $160~MHz$, the feed resonance occur at slightly higher frequencies. Notable are the difference in the shape of the resonant peaks. While the simulated response shows very wide resonant peaks, as expected from this dipole structures, the measured return loss of the feed has a narrow peak around its low frequency resonance. This feature dominates the fall off rate in the delay response of the system bandpass. The delay response of the feed is shown in figure \ref{ds_feed_on_dish_trans}. \begin{figure*}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_feed.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_feed.png}
\end{minipage}
\vspace{0.1cm}  
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_dish.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_HERA.png}
\end{minipage}
\caption{Upper panel: Magnitude and phase of the return loss of the feed as simulated and measured. Both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band. Lower panel: Magnitude and phase of return loss when the feed is suspended at the focal point of the dish which 5~m above the dish vertex.}   
\label{RL_mag_dish}
\end{figure*}

@@

\subsection{Dish reflections}
Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish. Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays. The estimated delay spectrum of the instrument is collectively contributed by all the reflections. Delay spectrum estimated from the return loss measurement of the feed alone,  provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish. 
From figure \ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by the feed structure. Therefore, the delay spectrum in both the cases follow each other. Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$. Hence, the dish reflection is expected to manifest themselves at an integral multiple of $30~ns$. The diameter of the feed cavity is $172~cm$  that results in signal reflections every integral multiple of $\approx2.86~ns$. The combined effect of feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the dish reflections starts to dominate and the two delay spectrum deviates from each other. With some manipulation of the equation \ref{eq10}, we can estimate the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in the figure \ref{dish_delay_spectrum}.

\subsection{Multiple reflection between the feed and the backend.}
Another effect that spill over of the smooth foreground power at higher delays is the multiple reflection of the received signal between the feed output and the input of the analog backend and correlators. In our measurements, the feed output is connected to the VNA via a 50 feet long LMR 400 cable. This length correspond to a delay of $\approx 120~nS$ for the signals travelling through the cable. The delay spectrum of both feed and feed-dish assembly shows an enhanced feature at this delay indicating a reflection from the VNA input. We measure the VNA input reflections by disconnecting the feed and connecting an open load at the feed input of the cable. The measured return loss is shown in the figure \ref{fig:open_RL}. Since the electromagnetic wave travelling through a transmission line undergoes a $100\%$ reflections from an open ended transmission line, we compute the combined effect of the VNA input return loss along with the cable resistive loss from this measurement as shown in figure \ref{fig:open_RL}. This results an important system design criterion for HERA. The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across the measurement band. This is consistent with the matched provided by the commercially available RF connectors that are commonly used. This manifests itself in a peak in the delay spectrum which is $50~dB$ above the measurement noise floor. The delays at which this effect becomes dominant depends on the length of the cable. Due to finite return loss at the input of the backends, this effect will be present in all the observations and thus would impact the instrument delay spectrum. However, its effect could be reduced below the level where the foreground  achieving a return loss at the backend input is greater than at least $-30~dB$.

@@

\subsection{Measurement bandwidth and window function}
Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements. Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function. In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays. Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data. Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window. Windowing the data prior to Fourier transform significantly reduces the system response higher delays.  
\begin{figure}
\centering
\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz. Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window. The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
\label{fig:window}
\end{figure}

%While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatched impedance between the feed and the 50 Ohm transmission line. In the delay domain, this appears at the zero delay bin. This response is identical whether or not the feed is suspended on the dish. We can, therefore, quantify this response by measuring the feed return loss while the feed is kept on the ground facing the sky. This results in a feed return loss including the surrounding cage structure but excluding the dish response. While a fraction, $\Gamma_{f}$, of the power is reflected off the feed, $1+\Gamma_{f}$ gets transmitted. In the receiving mode, upon initial incidence, $\Gamma_{f}$ of the voltage is reflected back into free space while $1+\Gamma_{f}$ enters the feed, and, in the delay domain, this appears at the zero delay bin. Using the return loss measurement of the feed $(\Gamma_{f})$ and the return loss measurement, $s_{11}$, of the dish, the feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component, and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. 
%
%
%\begin{figure}[ht]
%\centering
%\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
%\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output. The HERA feed design is driven by the PAPER element with an improved response at all delays. The feed, when suspended on the dish, results in a more complex return loss, and the corresponding delay response is shown in the figure.} %Delay units are incorrect!!!! Should be ns not GHz!!!!
%\label{fig:delay_spectrum}
%\end{figure}
\subsection{Delay spectrum of sub bands}
The dominant term in the expression of  return loss of the HERA element in receiving mode (\ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. As mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two resonances in between 100-140~MHz and 160-200~MHz. While the one at high frequency is a wider peak, the low frequency resonance shows a sharp feature in frequency. This dominates the overall shape of the delay spectrum in figure \ref{ds_feed_on_dish_trans}.\\
Also, In HERA analysis, the 21~cm power spectrum is estimated by gridding the observed data along the line of sight distance i.e is in frequency or redshift and spatial frequency scale $k$~\citep{liu_et_al2014a}. At particular redshift, the bandwidth of observation is so chosen that over the corresponding $\Delta z$, the 21~cm signal does not significantly evolve. Typically, the the 21~cm brightness temperature fluctuation evolve over redshift scale $\Delta z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}. Hence, the delay spectrum is estimated over smaller bandwidths.\\ 
We estimate the instrument delay spectrum over various sub bands between 100 to 200~MHz as shown in figure \ref{ds_full_sub_band}. Each panel of figure \ref{ds_full_sub_band} shows the delay spectrum estimated from the returnloss measurement of the HERA element between 100-200, 100-140, 140-160, 160 to 200~MHz respectively. Each panel also compares the estimated delay spectrum with two simulated delay spectra. The blue curve is the delay spectrum estimated from the simulated return loss of the feed and the feed-dish assembly that is shown in figure \ref{ds_feed_on_dish_trans}. Sub band delay spectra are wider compared to full band delay spectrum.  Shape of the resonant peaks determines the roll of rate of the delay spectrum in the range of 100-140~MHz and 160~200MHz. At higher frequency, our measurements closely follows the em simulations except around 120~ns where the cable reflection between the antenna and the backend manifests itself at all frequencies. \\

>>>>

% XXX document map
The efficacy of the techniques of foreground removal from the measured data
critically limits the 21~cm power spectrum measurements. The delay
transformation technique of foreground removal, introduced by
~\citep{Parsons_Backer_2009},\citep{Parsons_et_al_2012}, computes the Fourier
transform of the visibility measured by an interferometer and produces a
spectrum, referred to as the delay spectrum hereafter, which is a function of
the geometric time delay corresponding to the physical length of the baseline
between two antennas. For the visibilities measured over a wide field across a
wide frequency bandwidth, the delay spectrum consists of the instrument
response, the foreground signal, and the 21cm power spectrum, hereafter
referred to as the EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground
and for a widefield wide bandwidth visibility measurement by an interferometer
with a baseline $b$, confines the foreground contribution to the computed delay
spectrum within the largest possible time delay, $\tau = b/c$, corresponding to
the given baseline length. Such techniques also assume a spectrally smooth
instrumental response whose contribution to the measured data, much as the
contribution of the smooth spectrum foreground, also has an upper bound in the
delay space imposed by the largest geometric delay of the given baseline.
Beyond this limit, for an ideal system performance, the delay spectrum would be
dominated by any wideband signal across the sky with spectral and spatial
fluctuations over small scales, such as the EoR signal, and therefore, could be
detectable. The interaction between the sky signal and instrument response can
alter the relative contribution of the foreground, instrument response and the
EoR signal at a given delay and, thus, influence the detectability of the EoR
signal. Such interactions may cause the foreground and systematics to spill
over into higher delays and, thus, push the upper limit of the foreground and
systematics contaminated delay modes to much higher delays. In this process,
the EoR signal over large spatial scales will be lost. \\

\indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array
consisting of 568 14-m dishes in South Africa which will measure the 21~cm
power spectrum between 100 to 200~MHz.
In this paper, we investigate the performance of an individual HERA element and
the resulting manifestation of the instrument response to the delay spectrum.
Reflectometry measurements  are carried out across a wide bandwidth on a
prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the
results are interpreted in light of the delay spectrum technique of power
spectrum estimation and inverse covariance weighting method of foreground
suppression. Section 2 briefly describes the delay spectrum for the ideal and
non-ideal performance of a two element interferometer. Section 3 describes the
reflectometry measurements and establishes the connection between visibility
measurements and reflectometry. Reflectometry results are described in section
5. Section 6 evaluates the performance of the HERA element for detection of the
21~cm power spectrum.

This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}. We compare 
reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}. 
\begin{figure*}
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
\caption{HERA dish feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure*}

@@

\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}

The Hydrogen Epoch of Reionization Array consists of parabolic dishes which
provide increased collecting area per array element compared to its predecessor
experiment PAPER. Plane waves incident on a parabolic dish are focussed at the
feed which is kept at the focal plane of the dish.  The mismatch between the
impedance of free space and the feed and transmission line results in a partial
coupling of the sky signal into the feed while the rest is reflected off the
feed.  The reflected signal illuminates the dish and most of it is reflected
back into the space.  However, a part of it reflects back and forth several
times in between the feed and the vertex of the dish which is shadowed by the
feed.  Such reflections generate multiple copies of the incident sky signal of
reduced strength at various delay and phase and thus produces spurious
correlations in the visibilities of interferometric data.  Identical spurious
visibilities could be resulted due to reflections internal to the system
causing delay space distortion. Therefore, it is necessary to measure and
understand the instrument delay spectrum in order to qualify the system for the
measurement of 21cm power spectrum.  In this section we compute the visibility
of a two element interferometer accounting for the additional reflections of
the sky signal in between the feed and the dish vertex and the corresponding
effects on the delay spectrum in detail. We assume two antennas with identical
geometry and electrical parameters i.e,
$\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.

 \subsection{Antenna Reception With Multiple Reflections}
\label{sec:multiple}

To examine the performance of an antenna and feed in the presence of multiple
reflections, we can think of the system as a screen at a distance $F$ from a
feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern
of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage
and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed
reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern
$\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$
is coupled into the cable leading from the feed.  Additionally, however, the
voltage pattern is reflected off the feed ($\Gamma_f$), then the dish
($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a
roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$
times in between the feed and the dish, the net voltage entering the feed after
the $n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\label{eq6}
\end{eqnarray}

@@

Reflectometry measurements are carried out at the HERA element prototype in
Green Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument
response of the feed and dish assembly and characterise the performance.  HERA
element consists off a $14\,m$ diameter parabolic reflector and a
crossed-dipole pair as a feed. The cross dipole antenna pair is identical to
the feed of the PAPER antenna which is suspended at the focal plane of the dish
with the support of three vertical poles. HERA elements are closely spaced with
centre to centre distance between two dishes are equal to the dish diameter.
Therefore, to reduce the coupling between the adjacent dishes, the crossed
dipole feed along with the back plane is encased in a cylindrical cage. The
feed is raised and lowered by a three-pulley system mounted on the three poles.
The focal height of the dish is $5m$.  The detail geometry and electromagnetic
design of of the feed is presented in deBoer et al 2016. \\

%A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.

@@

\section{\textbf{Results}}
%Return loss measurements yields the instrument pass band response that would manifest in autocorrelation data of a single HERA element. Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.

Performance of the HERA feed and the dish-feed assembly has been simulated by
the em solver "High Frequency Structural Simulator(HFSS)" using the finite
element method.  The simulated and measured return loss of the feed, both
magnitude and phase are shown in the upper panel of the figure
\ref{RL_mag_dish}. While the simulated return loss of the feed structure shows
two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
slightly higher frequencies. Notable are the difference in the shape of the
resonant peaks. While the simulated response shows very wide resonant peaks, as
expected from this dipole structures, the measured return loss of the feed has
a narrow peak around its low frequency resonance. This feature dominates the
fall off rate in the delay response of the system bandpass. The delay response
of the feed is shown in figure \ref{ds_feed_on_dish_trans}.

\begin{figure*}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_feed.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_feed.png}
\end{minipage}
\vspace{0.1cm}  
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_dish.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_HERA.png}
\end{minipage}
\caption{Upper panel: Magnitude and phase of the return loss of the feed as simulated and measured. Both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band. Lower panel: Magnitude and phase of return loss when the feed is suspended at the focal point of the dish which 5~m above the dish vertex.}   
\label{RL_mag_dish}
\end{figure*}

@@

\subsection{Dish reflections}

Measurement equations shows the effects of multiple reflections of the sky
signal between the feed and the dish. Any other reflections off the feed
structure and/or any other part of the dish-feed assembly would appear at
arbitrary delays. The estimated delay spectrum of the instrument is
collectively contributed by all the reflections. Delay spectrum estimated from
the return loss measurement of the feed alone,  provides the lowest limit of
the delay spectrum of the instrument considering there is no multiple
reflections in between the feed and the dish.  From figure
\ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by
the feed structure. Therefore, the delay spectrum in both the cases follow each
other. Since the distance between the feed and the dish is 5 m, the roundtrip
delay between the dish and the feed as about $30~ns$. Hence, the dish
reflection is expected to manifest themselves at an integral multiple of
$30~ns$. The diameter of the feed cavity is $172~cm$  that results in signal
reflections every integral multiple of $\approx2.86~ns$. The combined effect of
feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the
dish reflections starts to dominate and the two delay spectrum deviates from
each other. With some manipulation of the equation \ref{eq10}, we can estimate
the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
the figure \ref{dish_delay_spectrum}.

\subsection{Multiple reflection between the feed and the backend.}

Another effect that spill over of the smooth foreground power at higher delays
is the multiple reflection of the received signal between the feed output and
the input of the analog backend and correlators. In our measurements, the feed
output is connected to the VNA via a 50 feet long LMR 400 cable. This length
correspond to a delay of $\approx 120~nS$ for the signals travelling through
the cable. The delay spectrum of both feed and feed-dish assembly shows an
enhanced feature at this delay indicating a reflection from the VNA input. We
measure the VNA input reflections by disconnecting the feed and connecting an
open load at the feed input of the cable. The measured return loss is shown in
the figure \ref{fig:open_RL}. Since the electromagnetic wave travelling through
a transmission line undergoes a $100\%$ reflections from an open ended
transmission line, we compute the combined effect of the VNA input return loss
along with the cable resistive loss from this measurement as shown in figure
\ref{fig:open_RL}. This results an important system design criterion for HERA.
The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across
the measurement band. This is consistent with the matched provided by the
commercially available RF connectors that are commonly used. This manifests
itself in a peak in the delay spectrum which is $50~dB$ above the measurement
noise floor. The delays at which this effect becomes dominant depends on the
length of the cable. Due to finite return loss at the input of the backends,
this effect will be present in all the observations and thus would impact the
instrument delay spectrum. However, its effect could be reduced below the level
where the foreground  achieving a return loss at the backend input is greater
than at least $-30~dB$.

@@

\subsection{Measurement bandwidth and window function}

Estimation of the delay spectrum by taking the Fourier transform of the
measured return loss is sensitive to the bandwidth of measurements. Since the
measurements are done in the spectral domain, measurement between two
frequencies is analogous to windowing the frequency domain data by a square
window function. In the delay domain, Fourier transform of this would result in
multiple side lobes at higher delays. Therefore, appropriate windowing of the
data is  necessary prior to taking the Fourier transform of the measured data.
Figure \ref{fig:window} shows the delay spectrum estimated from the measured
data using a square window as well as Blackman Harris window. Windowing the
data prior to Fourier transform significantly reduces the system response
higher delays.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz. Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window. The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
\label{fig:window}
\end{figure}

%While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatched impedance between the feed and the 50 Ohm transmission line. In the delay domain, this appears at the zero delay bin. This response is identical whether or not the feed is suspended on the dish. We can, therefore, quantify this response by measuring the feed return loss while the feed is kept on the ground facing the sky. This results in a feed return loss including the surrounding cage structure but excluding the dish response. While a fraction, $\Gamma_{f}$, of the power is reflected off the feed, $1+\Gamma_{f}$ gets transmitted. In the receiving mode, upon initial incidence, $\Gamma_{f}$ of the voltage is reflected back into free space while $1+\Gamma_{f}$ enters the feed, and, in the delay domain, this appears at the zero delay bin. Using the return loss measurement of the feed $(\Gamma_{f})$ and the return loss measurement, $s_{11}$, of the dish, the feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component, and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. 
%
%
%\begin{figure}[ht]
%\centering
%\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
%\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output. The HERA feed design is driven by the PAPER element with an improved response at all delays. The feed, when suspended on the dish, results in a more complex return loss, and the corresponding delay response is shown in the figure.} %Delay units are incorrect!!!! Should be ns not GHz!!!!
%\label{fig:delay_spectrum}
%\end{figure}
\subsection{Delay spectrum of sub bands}
